Turkey Hemorrhagic Enteritis Virus transcriptome profiling

### 2023-07-21 manuscript_thev_transcriptome.Rmd
Update scripts to generate pertinent info for manuscript

cov_4hr <- cov_thev %>% filter(timepoint == "4hpi") %>%
              select(total_mapped) %>% pull()
cov_72hr <- cov_thev %>% filter(timepoint == "72hpi") %>%
              select(total_mapped) %>% pull()
cov_72hr <- round(cov_72hr / 1e6, 1)

total_mapped <- round(sum(cov_thev$total_mapped) / 1e6, 1)

@@

```{r}
tab1 %>% 
  gt(rowname_col = "Metric") %>% 
  tab_header(title = md("**Table 1**"),
             subtitle = "Summary of sequence alignment metrics") %>%
  opt_align_table_header(align = "left") %>% 
  fmt_number(suffixing = T,
             rows = everything(),
             columns = everything()) %>% 
  cols_width(Metric ~ px(150)) %>% 
  opt_row_striping(row_striping = T) %>% 
  tab_options(table.layout = "auto",
              table.align = "left",
              column_labels.font.size = "18px",
              column_labels.font.weight = "bold",
              table_body.vlines.style = "solid") %>% 
  tab_stubhead(label = md("Metric"))

>>>>

cov_4hr <- cov_thev %>% filter(timepoint == "4hpi") %>%
              select(total_mapped) %>% pull() %>% as.numeric(.)
cov_72hr <- cov_thev %>% filter(timepoint == "72hpi") %>%
              select(total_mapped) %>% pull() %>% as.numeric(.)
cov_72hr <- round(cov_72hr / 1e6, 1)

total_mapped <- round(sum(as.numeric(cov_thev$total_mapped)) / 1e6, 1)

@@

```{r}
tab1 %>% 
  gt(rowname_col = "Metric") %>% 
  tab_header(title = md("**Table 1**"),
             subtitle = "Summary of sequence alignment metrics") %>%
  opt_align_table_header(align = "left") %>%
  cols_width(Metric ~ px(150)) %>% 
  opt_row_striping(row_striping = T) %>% 
  tab_options(table.layout = "auto",
              table.align = "left",
              column_labels.font.size = "18px",
              column_labels.font.weight = "bold",
              table_body.vlines.style = "solid") %>% 
  tab_stubhead(label = md("Metric"))
